\section{Conferences AND Workshops}




\outerlist{


\entrybig[\textbullet]
{\link{https://indico.fnal.gov/event/59091/}{\textbf{SM@LHC 2023 
}} (July, 2023)}{}
{The SM@LHC workshop deals with the latest developments as well as future prospects in Standard Model phenomenology at the LHC.}{}


\entrybig[\textbullet]
{\link{https://indico.cern.ch/event/1196111/}{\textbf{IRIS-HEP Institute Retreat (Princeton University) 
}} (October, 2022)}{}
{Annul checkpoint the status of the IRIS-HEP efforts to date and specific plans and achievable goals for the next year .}{}

\entrybig[\textbullet]
{\link{https://conf.slac.stanford.edu/ssi2022/}{\textbf{SLAC Summer Institute 2022 - (SSI 2022)
}} (August, 2022)}{}
{Annual event by SLAC aims to inform graduate students and post-docs about latest developments in the field.}{}



\entrybig[\textbullet]
{\link{https://indico.cern.ch/event/1128662/}{\textbf{Fourth Computational and Data Science school for HEP (CoDaS-HEP 2022)
}} (August, 2022)}{}
{The CoDaS-HEP school aims to provide a broad introduction to these critical skills in Computational High Energy Physics.}{}


\entrybig[\textbullet]
{\link{https://indico.cern.ch/event/1128662/}{\textbf{Searching for Long-Lived Particles - Eleventh Workshop of the LLP Community
}} (June, 2022)}{}
{The eleventh LLP Community workshop discussing current and future searches of LLPs.}{}



\entrybig[\textbullet]
{\link{https://indico.fnal.gov/event/51844/}{\textbf{Snowmass Rare and Precision Measurements Frontier Spring Meeting
}} (May, 2022)}{}
{DESY offers students in physics the possibility to participate in the research activities through this program.}{}


\entrybig[\textbullet]
{\link{https://indico.cern.ch/event/1031398/}{\textbf{DESY Summer Student Programme 2021
}} (July-September, 2021)}{}
{The meeting is part of snowmass process discussing highest prospects for uncovering New Physics over the next ten years.}{}


\entrybig[\textbullet]
{\link{https://indico.cern.ch/event/1031398/}{\textbf{CMS Open Data Workshop 2021
}} (July, 2021)}{}
{The workshop aims to bridge the technical gap of a full analysis with CMS open data.}{}

\entrybig[\textbullet] 
{\link{http://win2021.umn.edu/}{\textbf{The 28th International Workshop on Weak Interactions and Neutrinos}} (June, 2021)}{} 
{Assess the status of the field and to initiate collaborative efforts to address current physics questions.}{} 


\entrybig[\textbullet]
{\link{https://indico.cern.ch/event/959266/}{\textbf{Beyond Standard Model: From Theory to Experiment (BSM- 2021)}} (March, 2021)}{}
{ Discuss latest developments in the physics beyond the standard models of particle physics, cosmology and gravitation.}{}


\entrybig[\textbullet]
{\link{https://indico.cern.ch/event/924283/}{\textbf{Fast Machine Learning for Science Workshop}} (Oct, 2020)}{}
{ Discuss emerging methods and scientific applications for deep learning and inference acceleration applications in HEP.}{}

\entrybig[\textbullet]
{\link{https://www.gw-openscience.org/s/workshop3/index.html/}{\textbf{Gravitational-Wave Open Data Workshop \#3}} (May, 2020)}{}
{ Intended for scientists and students who wish to learn about using gravitational-wave data and software.}{}


}



